Model Search in Relational Domains

### 2016-10-22 experiments.tex
solver name

\begin{table}[t]
\begin{center}
{
\begin{tabular}{l|r|r|r|r|r}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\ \hline
SAT & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\end{table}

>>>>

\begin{table}[t]
\begin{center}
{
\begin{tabular}{l|r|r|r|r|r}
\hline
Solver & Decisions & propagations & conflict & conflict literals & restarts \\ \hline
MiniSat & 27917 & 304031 & 3949 & 33646 & 64 \\ \hline
ACDCL (Product Domain) & 161 & 3130 & 10 & 5 & 0 \\ \hline  
\end{tabular}
}
\end{center}
\caption{Solver statistics}
\label{result}
\end{table}
